### 2014-07-14 paper/introduction.tex
per chair

Recently, human-computer interaction researchers have begun to explore how to prototype interactive objects using additive 3D printing processes.
\changes{Existing approaches, including Printed Optics \cite{Willis-printedoptics} and Sauron \cite{Savage-sauron}, exclusively focus on optical sensing and visual displays --- we seek to grow the vocabulary of supported tangible input and output modalities, and we propose using pipes and cavities, allowing designers to integrate secondary materials post-print, for this purpose.}

>>>>

\changes{Recently, human-computer interaction researchers have begun to explore how to add interaction to 3D printed objects by creating appropriate structures inside those objects. They have introduced techniques such as printed light pipes~\cite{Willis-printedoptics} and printed hollow chambers for air pressure sensing~\cite{slyper}. These projects introduce point examples of particular techniques. In this paper we present a systematic design space of using 3D printed pipes and cavities, and introduce a design tool that enables makers to add interactivity to their models through internal pipes.}
